Technical Report

### 2017-10-27 fully-abstract-comp/technical-report.tex
A bit more text about the proposed worlds

\section{Logical Relation}
\subsection{Worlds}
\[
  \World = \RegionName \parfun 2 \times \Region
\]
where $\RegionName = \nats$
\[
  \Region = \left\{
  \begin{array}{l}
    \{\pureReg \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})\\
    \{\normalReg \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})\\
  \end{array} \right.
\]
\lau{26-20-2017: It is not clear to me what the monotonicity requirements on the memory interpretation functions should be.}
\[
  W_1 \uplus W_1 = W
  \begin{array}[t]{l}
    \text{if $\dom(W) = \dom(W_1) = \dom(W_2) \tand$} \\
    \forall r \in \dom(W) \ldotp W(r) = W_1(r) \oplus W_2(r)
  \end{array}
\]
$\oplus$ is defined as follows
\begin{align*}
  (i,\normalReg,\var{sm}) \uplus (j,\normalReg,\var{sm}) = & (\max(i,j),\normalReg,\var{sm}) \\
  (1,\pureReg,\var{sm}) \uplus (0,\pureReg,\var{sm}) = & (1,\pureReg,\var{sm}) \\
  (0,\pureReg,\var{sm}) \uplus (1,\pureReg,\var{sm}) = & (1,\pureReg,\var{sm}) \\
  (0,\pureReg,\var{sm}) \uplus (0,\pureReg,\var{sm}) = & (0,\pureReg,\var{sm}) \\
\end{align*}
and for all other cases $\oplus$ is undefined. Specifically, $\uplus$ is not defined when both sides are an owned $\pureReg$-region. It is further not defined if the two sides do not agree on region type and state machine.

>>>>

\section{Logical Relation}
\subsection{Worlds}
\[
  \World = \RegionName \parfun 2 \times \Region
\]
where $\RegionName = \nats$. $2$ indicates ownership of the region which decides whether a capability is allowed to reference this part of memory.
\lau{26-10-2017: Maybe we want to place the ownership directly on the $\pureReg$-regions as we only want to enforce that linear capabilities don't have any aliases.}
\[
  \Region = \left\{
  \begin{array}{l}
    \{\pureReg \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})\\
    \{\normalReg \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})
  \end{array} \right.
\]
\lau{26-20-2017: We may also want to build the infrastructure for the stack more explicitely into the worlds (but maybe we can handle it in the memory satisfaction).}
\lau{26-20-2017: It is not clear to me what the monotonicity requirements on the memory interpretation functions should be.}

Disjoint union of worlds. Joins together two alike worlds with strictly disjoint ownership over $\pureReg$-regions.
\[
  W_1 \uplus W_1 = W
  \begin{array}[t]{l}
    \text{if $\dom(W) = \dom(W_1) = \dom(W_2) \tand$} \\
    \forall r \in \dom(W) \ldotp W(r) = W_1(r) \oplus W_2(r)
  \end{array}
\]
$\oplus$ is defined as follows
\begin{align*}
  (i,\normalReg,\var{sm}) \uplus (j,\normalReg,\var{sm}) =  & \; (\max(i,j),\normalReg,\var{sm}) \\
  (1,\pureReg,\var{sm}) \uplus (0,\pureReg,\var{sm}) =      & \; (1,\pureReg,\var{sm}) \\
  (0,\pureReg,\var{sm}) \uplus (1,\pureReg,\var{sm}) =      & \; (1,\pureReg,\var{sm}) \\
  (0,\pureReg,\var{sm}) \uplus (0,\pureReg,\var{sm}) =      & \; (0,\pureReg,\var{sm}) \\
\end{align*}
and for all other cases $\oplus$ is undefined. Specifically, $\uplus$ is not defined when both sides are an owned $\pureReg$-region. It is further not defined if the two sides do not agree on region type and state machine.
